---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

```{r}
fit <- stan_glm(data = week_12,
                age ~ sex + solo + primary_04 + primary_06 + treatment + sex:solo,
                refresh = 0)
```

age ~ sex + solo + primary_04 + primary_06 + treatment + sex:solo
                    
* Is this a causal or predictive model? Why?
predictive model; we can't really change our age no matter what we do.

* Interpret the fitted model. 
intercept: age of the average age for women do not live alone who did not vote in the primary and did not receive any treatment
male: predicted change in outcome: if you are a man who does not live alone and vote in the primary and did not receive any treatment, add that value to the intercept to get your age
solo alone: if you are a female who lived alone and did not have any treatment, you add that value to your age
interaction term: you can have the slope of men who live alone compared to women who live alone; we are holding male constant;


* Should we keep all these variables? And the interaction term?

* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?




## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)







